Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-30 article/draft.tex
remove the disappeared information panel

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
{\color{red} [ADD Vaccine hesitancy screenshot]}

@@

@@

\begin{table}[h] 
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
\makecell{Without \\ any \\ panel} & 
\makecell{With a \\ `COVID-19' \\ panel} & 
\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
\makecell{With a \\ `climate change' \\ panel} &
\makecell{With a \\ `U.S. elections' \\ panel} &
\makecell{With a \\ `vaccine hesitancy' \\ panel}  
\\ \hline
\makecell{74 \\ (44 \%)} &
\makecell{71 \\ (42 \%)} &
\makecell{19 \\ (11 \%)} &
\makecell{4 \\ (2 \%)} &
\makecell{1 \\ (0.5 \%)} &
\makecell{1 \\ (0.5 \%)}
\\ \hline
\end{tabular}
\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
\label{youtube_panel_proportions}
\end{table}

@@

\begin{figure}[h]
	\centering
		\begin{multicols}{1}
		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png} &
		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 
		\end{multicols}
		%\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}
		%\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
Left panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
Right panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
	\label{duplicates_yt}
\end{figure}

>>>>

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
Four types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19 and US elections, as shown in figure \ref{youtube_panel_screenshots}.

@@

\begin{table}[h] 
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
\makecell{Without \\ any \\ panel} & 
\makecell{With a \\ `COVID-19' \\ panel} & 
\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
\makecell{With a \\ `climate change' \\ panel} &
\makecell{With a \\ `U.S. elections' \\ panel}  
\\ \hline
\makecell{75 \\ (44 \%)} &
\makecell{71 \\ (42 \%)} &
\makecell{19 \\ (11 \%)} &
\makecell{4 \\ (2 \%)} &
\makecell{1 \\ (0.6 \%)}
\\ \hline
\end{tabular}
\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
\label{youtube_panel_proportions}
\end{table}

@@

@@

\begin{figure}[h]
	\centering
		\begin{multicols}{1}
		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png}
		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 
		\end{multicols}
		%\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}
		%\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
Left panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
Right panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
	\label{duplicates_yt}
\end{figure}
